\thispagestyle{empty}
\begin{center}
\textsc{\normalfont\Huge\bfseries\color{document}Abstract} 
\end{center}
\newcommand{\abstractkey}{This work proposes to use a combination of Semantic Web concepts, including consistency, inferencing, and constraints to detect premature information. We calculate the information maturity-level and present it using well-known data presentation concepts. We propose the decision design pattern to reduce the time and expertise domain experts need to build Semantic Web-based ontologies that can detect premature information and present the information maturity-level. Additionally, the transparent information maturity-level helps decision-makers to move from intuition-based decision-making to evidence-based decision-making.}

\abstractkey 

% Samenvatting, maximaal 200 woorden
Decisions, especially in the software product management discipline, are mostly complex and made based on intuition due to missing information or the lack of time to analyse the available information. A software product manager can understand if \emph{this} is the right time to make \emph{that} decision by understanding the information maturity-level of the decision-relevant information.

The decision design pattern calculates the information maturity-level using the completeness, reproducibility, consensus, and conflict violations. We detect the completeness, reproducibility, consensus, and conflict violations using Semantic Web constraints. Domain experts can re-use the decision design pattern and apply it for their decisions. Based on the presentation of the information maturity-level, the decision-maker can decide to continue the decision-making process or elaborate on the information.
 
We need to have the domain knowledge to validate the Semantic Web constraints. Therefore, we use two decisions from the software product management domain to validate our approach: requirement prioritisation and alternative solution selection. We create a supporting ontology structure for both decisions and instantiate the decision design pattern.

\noindent\textsc{\normalfont\large\bfseries\color{document}Key terms} \hfill \break
Evidence-based management; EBM; generic ontology design pattern; GODP; software product management; SPM; decision making; ontology design pattern; constraints; SHACL; Semantic Web.  

\vspace*{\fill} 

