% Title
\newcommand{\researchname}{a decision design pattern to detect and present the maturity-level of decision-relevant information}

% Main research question
\newcommand{\researchquestion}{$RQ$: To what extent can the detection of premature information using SHACL Semantic Web constraints contribute to evidence-based decision-making?}

% Help = too vague.
% Increase, reduce = needs to be measurable.
% Motivate = keyword that needs to be clearly defined.

% Validation
\newcommand{\valone}{$VAL1$: To what extent can the detection of premature information using SHACL Semantic Web constraints contribute to evidence-based requirements prioritisation?}
\newcommand{\valtwo}{$VAL2$: To what extent can the detection of premature information using SHACL Semantic Web constraints contribute to evidence-based alternative solution selection?}

% Theoretical framework
\newcommand{\tfone}{$TF1$: How are decision-makers making decisions?} % Evidence-based management, information is never complete. Which types of decisions? Binary, numeric?
\newcommand{\tftwo}{$TF2$: When is decision-relevant information premature?} % Completeness and reliability of information. Depends on the context.
\newcommand{\tfthree}{$TF3$: To what extent can we detect premature information?} % semantic web, application logic. How can Semantic Web technologies practically interact with application logic?
\newcommand{\tffour}{$TF4$: What is the impact of the presentation of the information maturity-level on a decision?} % Visualization of information. Show impact of the decision on the information?
\newcommand{\tffive}{$TF5$: To what extent can we generalise our approach?} % Ontology / UI Design patterns 

% Data structuur
\newcommand{\rqdsone}{$DS1$: To what extent can we create a generic ontology design pattern for evidence-based management?}
\newcommand{\rqdstwo}{$DS2$: To what extent can we store the information completeness and reliability in an (extended) evidence-based management ontology?}
\newcommand{\rqdsthree}{$DS3$: To what extent can we use Semantic Web inferencing, consistency, and constraints to detect premature information?}

% Visualization
\newcommand{\rqvisone}{$PRES1$: How do we define the maturity-level of decision-relevant information?}
\newcommand{\rqvistwo}{$PRES2$: Under which circumstances is a decision-maker interested in the maturity-level of decision-relevant information?}
\newcommand{\rqvisthree}{$PRES3$: To what extent can we make it easier for a decision-maker to understand the maturity-level of decision-relevant information?}
