\section{Validation} \label{validation}
The decision ontology pattern consolidates the completeness, reproducibility, consensus, and conflict patterns. These patterns are useful on their own. However, only their consolidation, combined with the evidence-management pattern, contributes to the answer to our research question. Therefore, we validate the consolidated decision ontology pattern in this chapter. Additionally, we also validate the decision presentation pattern in this chapter. 

We use two scenarios to validate the decision ontology pattern and decision presentation pattern:
\begin{enumerate}
\item \nameref{val-rp}
\item \nameref{val-as}
\end{enumerate}

The goal of the first scenario is to prove the decision design pattern leads to the expected results. The goal of the second scenario is to prove that the decision design pattern can be applied in other scenarios as well. We limit the validation depth of the second scenario when there is an overlap with the first scenario. 

These scenarios are related to each other. A software product manager first prioritises the requirements in his backlog. Each requirement specifies a problem to solve or a goal to reach. Once the product team picks a requirement for implementation, the product team uses alternative solution selection to select the right technical solution to solve the specified problem or reach a specific goal. Both scenarios have challenges that attract the interest of academics. We use these scenarios as examples for which the decision design pattern increases the transparency of the information maturity-level. Software product managers can use this transparency to evaluate if the information is ready to make an evidence-based decision.

\input{VAL-RP} % Validation of the concept in the context of requirements prioritisation.
\input{VAL-AS}