\thispagestyle{empty}
\begin{center}
\textsc{\normalfont\Huge\bfseries\color{document}Acknowledgement} 
\end{center}
Studying has been a significant part of my life since I started with this journey in 2011. In the meantime, I started working at Bosch, the German industrial giant and moved to the south of Germany. This job challenges me every day and brings me to exciting parts of the world. It was quite a challenge to keep this up for almost ten years, but I made it. 

My initial goal was to finish this study before my 30\textsuperscript{th} birthday. Unfortunately, I was not able to achieve this goal. At the same time, the learning experience was more important for me than keeping the schedule. I have no regret from restarting several courses, including the graduation assignment, and taking my time to understand what is going on. My goal is to learn, not to impress.

The inspiration for the subject of this graduation assignment came from my work environment. I observed that we made several complex and high-impact decisions using information that was based on opinions and open for interpretation. Taking the complexity of the job, product, and market into account, I felt there should be a more structured approach to take these decisions. We, Lloyd and I, discussed the potential to use the Semantic Web to address parts of this challenge, which intrigued me.

Even though they are probably responsible for messing up my schedule, staying close to my family and friends contributed to this result. The everyday distractions they caused, the weekends travelling to the Netherlands driving 160km/h on the autobahn for six hours, the long Oktoberfest weekends, and the countless trips to the Alps kept me alive during these ten years. Lloyd kept me focused during the graduation assignment itself, and provided a continuous stream of guidance during our regular appointments, while Bastian shared his outside-in perspective. Finally, effective tooling also helps. Skype only failed me once in the last couple of months, Grammarly improved my writing skills, and Spotify shared countless hours of motivation. 

Thank you for your support.

Mario

\vspace*{\fill} 