\makeglossaries
\makeindex

\newglossaryentry{control_system}
{
name=control system,
description={A control system is able to influence the behaviour of devices or (sub)systems}
}
\newglossaryentry{strategy}
{
name=strategy,
description={A strategy is generally defined as a method or plan to achieve a specific goal or solve a specific problem, where as an algorithm is generally defined as a mathematical or logical specification of how to solve one or multiple problems. An algorithm could be considered being a strategy to reach a specific goal, or solve a specific problem.}
}

\newglossaryentry{goal}
{
name=goal,
description={A control system is build to solve a problem or, from a different perspective, reach a specific goal. In order to reach that goal, the control system (and it's connected devices) consumes energy.}
}

\newglossaryentry{hybrid_system}
{
name=hybrid system,
description={In the context of this study a hybrid system is a system which uses a combination of hardware and software to reach a specific system state.}
}

\newglossaryentry{overhead_consumption}
{
name=overhead,
description={Overhead is consumed by the control system itself, but at the same time it does not contribute to a specific goal. It equals the total amount of energy consumed by the system minus the specific amount of energy that is consumed to reach a specific goal}
}

\longnewglossaryentry{renewable_energy}
{
name=renewable energy
}
{
Energy from renewable sources is defined by \cite{RE1} as: 
\begin{quote}energy from renewable sources’ means energy from renewable non-fossil sources, namely wind, solar, aerothermal, geothermal, hydrothermal and ocean energy, hydropower, biomass, landfill gas, sewage treatment plant gas and biogases;\end{quote}
}
\newglossaryentry{problem_instance}
{
name=problem instance,
description={Each problem can have several instances, depending on the environment in which the problem needs to be solved.}
}

\newglossaryentry{environment}
{
name=environment,
description={The environment (of the system) cannot be influenced by the system itself. Examples: the weather, the amount of people in a room.}
}

\newglossaryentry{system_state}
{
name=system state,
description={The system state can be influenced by the system itself, either directly (by controlling connected devices and sensors) or indirectly (by using the impact of the connected devices and sensors). Examples: (direct) switching on a pump, (indirect) increasing the temperature of a room.}
}

\newglossaryentry{primary_energy_sources}
{
name=primary energy sources,
description={\parencite{IM9} considers crude oil, natural gas, biomass and waste, coal, wind, solar, hydro-power, geothermal-power and ocean-power, and nuclear power (based on natural uranium) as \emph{primary energy sources}.}
}